Spatiotemporal transmission risk

### 2023-03-20 analysis/spatiotemporal-transmission-risk.Rmd
data, workflow and minor fixes

```{r}
selected_dates <- as.Date(list.files("../data-clean/Masi/patient-tracking-data")[-1])
```

@@

# share of TB patients
share_tb <- clinical_dta  %>%
  group_by(date, patient_id) %>%
  summarize(tb = any(tb_suspect == "yes")) %>%
  ungroup() %>%
  group_by(date) %>%
  summarize(n = n(),
            n_tb = sum(tb)) %>%
  arrange(date) %>%
  mutate(prop_tb = n_tb / n * 100,
         date = format(date, format = "%b %d"),
         date = factor(date, levels = unique(date))) %>%
  ungroup() 
share_tb_pl <- share_tb %>%
  ggplot(aes(x = date, y = n_tb)) +
  geom_bar(stat = "identity", fill = "grey", color = "black", width = .5) +
  annotate("text", x = "Nov 10", y = mean(share_tb$n_tb), label = paste0("Mean = ",round(mean(share_tb$n_tb), 1)), color = "darkred", size = 8 / cm(1), vjust = -1) +
  geom_hline(aes(yintercept = mean(share_tb$n_tb)), color = "darkred") +
  scale_y_continuous(expand = expansion(mult = c(0,0.05))) +
  scale_x_discrete(breaks = format(selected_dates, format = "%b %d")[c(1, 4, 8, 12)]) +
  labs(y = "No. of masked TB patients") +
  theme_classic() +
  theme(axis.title.x = element_blank(),
        plot.margin = margin(5.5, 5.5, 5.5, 5.5),
        text = element_text(size = text_descr))
ggsave(plot = share_tb_pl, filename = "../doc/IWHOD/presentation/figures/share-tb-patients.png", w = width_descr, h = height_descr)
```

@@

```{r}
co2_pl <- readRDS("../data-clean/Masi/environmental-data/co2-temp-humid.rds") %>%
  filter(location %in% c("waiting room", "tb room"),
         date %in% selected_dates) %>%
  mutate(location = factor(ifelse(location == "tb room", "TB room", "Waiting room"), levels = c("Waiting room", "TB room")),
         time = as.POSIXct(time, format = "%H:%M", tz = "CET")) %>%
  ggplot(aes(x = time, y = co2, color = location, fill = location)) +
  stat_lineribbon(alpha = .25, size = .75) +
  scale_x_datetime(expand = c(0,0), date_breaks = "2 hours", date_labels = "%H:%M") +
  scale_y_continuous(expand = c(0,0), breaks = scales::breaks_width(width = 100)) +
  scale_fill_manual(values = wes_palette("Moonrise2")) +
  scale_color_manual(values = wes_palette("Moonrise2")) +
  labs(y = expression("CO"[2]*" (ppm)"), fill = "Quantile", color = "Quantile") +
  theme_classic() +
  theme(legend.position = c(.65,.95), legend.direction = "horizontal", legend.key.width = unit(0.3, "cm"), legend.key.height = unit(0.2, "cm"),
        plot.margin = margin(5.5, 5.5, 5.5, 5.5), axis.title.x = element_blank(), legend.title = element_blank(),
        text = element_text(size = text_descr)) 
ggsave(plot = co2_pl, filename = "../doc/IWHOD/presentation/figures/co2-levels.png", width = width_descr, height = height_descr)
```

@@

# test
waiting_room_df$value <- rnorm(nrow(waiting_room_df))
passage_df$value <- rnorm(nrow(passage_df))
tb_room_df$value <- rnorm(nrow(tb_room_df))

ggplot(mapping = aes(x = long, y = lat, group = group, fill = value)) +
  geom_polygon(data = waiting_room_df) +
  geom_polygon(data = passage_df) +
  geom_polygon(data = tb_room_df) +
  ggpubr::background_image(clinic_img) +
  annotate("text", x = -13200, y = -5300, label = "Entrance", size = 8 / cm(1), fontface = 2, hjust=0,vjust=0) +
  annotate("text", x = -13400, y = -2300, label = "Waiting room", size = 8 / cm(1), fontface = 2, hjust=0,vjust=0) +
  annotate("text", x = -5000, y = -4100, label = "Registration", size = 8 / cm(1), fontface = 2, angle = 90, hjust=0,vjust=0) +
  annotate("text", x = 2600, y = -2700, label = "TB room", size = 8 / cm(1), fontface = 2) +
  scale_y_continuous(expand = expansion(add=c(2500, 4000))) +
  scale_x_continuous(expand = expansion(add=c(400, 500))) +
  labs(fill = "Density") +
  theme(axis.text = element_blank(), axis.title = element_blank(), axis.ticks = element_blank(),
        legend.position = c(0.825,0.075), legend.direction = "horizontal", legend.title = element_blank(), #legend.title = element_text(vjust = .75),
        panel.background = element_rect(fill = RColorBrewer::brewer.pal(n = 3, name = "YlOrRd")[1]), panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())
```

@@

```{r}
files <- list.files("../data-clean/Masi/patient-tracking-data/", full.names = T)[-1]
no_people <- do.call(rbind, lapply(files, function(x) readRDS(paste0(x, "/patient-id-data_matched-filtered.rds")))) %>%
  mutate(date = as.Date(format(time, format = "%Y-%m-%d")),
         time_min = as.POSIXct(format(time, format = "%H:%M"), format = "%H:%M"))

@@

# Spatial
no_people_spatial_pl <- no_people %>%
  ggplot(aes(x = x, y = y)) +
  geom_bin2d(binwidth = 100) +
  scale_fill_stepsn(colours = RColorBrewer::brewer.pal(n = 9, name = "YlOrRd"), trans = "log", breaks = c(1, 10, 100, 1000, 10000)) +
    ggpubr::background_image(clinic_img) +
    annotate("text", x = -13200, y = -5800, label = "Entrance", size = text_descr / cm(1), hjust=0,vjust=0) +
    annotate("text", x = -14000, y = -2600, label = "Waiting room", size = text_descr / cm(1), hjust=0,vjust=0) +
    annotate("text", x = -5800, y = -4500, label = "Registration", size = text_descr / cm(1), angle = 90, hjust=0,vjust=0) +
    annotate("text", x = 3000, y = -2700, label = "TB room", size = text_descr / cm(1)) +
    scale_y_continuous(expand = expansion(mult=c(0.05, 0.15))) +
    scale_x_continuous(expand = expansion(mult=c(0.03, 0))) +
    labs(fill = "Density") +
    theme(axis.text = element_blank(), axis.title = element_blank(), axis.ticks = element_blank(), legend.key.width = unit(0.3, "cm"), legend.key.height = unit(0.3, "cm"),
          legend.position = c(0.825,0.075), legend.direction = "horizontal",legend.title = element_text(vjust = .75),
          panel.background = element_rect(fill = RColorBrewer::brewer.pal(n = 9, name = "YlOrRd")[1]), panel.grid.major = element_blank(),
          panel.grid.minor = element_blank()) +
  guides(fill = guide_legend(title.position = "top", label.position = "bottom"))
ggsave(plot=no_people_spatial_pl, filename = "../doc/IWHOD/presentation/figures/no-people-spatial.png", width = width_descr, height = height_descr)
```

@@

```{r}
relQC_pl <- expand.grid(distance = seq(0, 10, .1), 
                           mu = rMuIc(n_samples)) %>%
  mutate(relQC = dIc(distance, mu) * 100) %>%
  ggplot(aes(x = distance, y = relQC)) +
  stat_lineribbon(alpha = .5, size = .5) +
  scale_x_continuous(expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0)) +
  scale_fill_brewer(palette = "OrRd") +
  labs(x = "Distance (m)", y = "Relative quanta concentration (%)", fill = "Quantile") +
  theme_bw2() +
  theme(legend.position = c(.8,.9), legend.direction = "horizontal", legend.key.width = unit(0.3, "cm"), legend.key.height = unit(0.2, "cm"),
        plot.margin = margin(5.5, 10, 5.5, 5.5)) +
  guides(fill = guide_legend(title.position = "top"))
save_plot(relQC_pl, pdf_file = "../results/inputs/spatial-relative-quanta-concentration.pdf", w = aw, h = ah)
```

@@

```{r}
sim_results <- list.files("../simulations/Masi/2021-10-25/", full.names = T)
sim_results <- do.call(rbind, lapply(sim_results, readRDS))
```

@@

```{r}
# individual patient transmission risk by simulation
transRisk <- sim_results %>%
  group_by(patient_id, sim) %>%
  slice(1) %>%
  ungroup()

# Average transmission risk across patients
transRisk_av <- transRisk %>%
  group_by(sim) %>%
  summarize(across(c(P_N, P_N_ns), mean)) %>%
  ungroup()

mean_risk <- round(mean(transRisk_av$P_N * 100), 1)
q25_risk <- round(quantile(transRisk_av$P_N * 100, .25), 1)
q75_risk <- round(quantile(transRisk_av$P_N * 100, .75), 1)
message(sprintf("Spatiotemporal transmission risk across clinical attendee: %s percent (IQR: %s to %s)", mean_risk, q25_risk, q75_risk))

# individual transmission risk across simulations
transRisk_indv <- transRisk %>%
  group_by(patient_id) %>%
  summarize(across(c(P_N, P_N_ns), list(mean = mean, median = median,q25 = function(x) quantile(x, .25), q75 = function(x) quantile(x, .75)))) %>%
  ungroup()

transRisk_indv_pl <- transRisk_indv %>%
  mutate(patient_id = factor(patient_id)) %>%
  ggplot(aes(x = reorder(patient_id, -P_N_mean), y = P_N_mean)) +
  geom_point(shape = 4, alpha = .5) +
  geom_hline(aes(yintercept = mean_risk / 100), color = "darkred") +
  geom_hline(aes(yintercept = q25_risk / 100), color = "darkred", linetype = "dashed") +
  geom_hline(aes(yintercept = q75_risk / 100), color = "darkred", linetype = "dashed") +
  annotate("text", x = 375, y = 0.0075, label = paste0("Average across patients = ", mean_risk, "% (IQR:", q25_risk, "-", q75_risk,")"),
           size = 8 / cm(1), color = "darkred") +
  scale_y_continuous(labels = function(x) x * 100, expand = expansion(mult = c(0., .05)), breaks = c(seq(0, 0.05, 0.01), 0.004)) +
  labs(y = "Mean risk of infection (%)", x = "Clinic attendee") +
  theme_bw2() +
  theme(axis.text.x = element_blank())
save_plot(transRisk_indv_pl, pdf_file = "../results/modeling/risk-of-infection.pdf", w = aw, h = ah)

# high risk of infection plot
group_labs <- c("Small (1-5%)", "Medium (5-10%)", "High (>10%)")
transRisk_qq <- transRisk %>%
  mutate(risk_cat = base::cut(P_N * 100, breaks = c(-Inf, 1, 5, 10, Inf), labels = c("negligible risk", group_labs))) %>%
  group_by(sim, risk_cat) %>%
  summarize(n = n()) %>%
  ungroup()
transRisk_MinorVsHigh <- transRisk_qq %>%
  mutate(risk_cat = ifelse(risk_cat == "negligible risk", "low", "high")) %>%
  group_by(sim, risk_cat) %>%
  summarize(n = sum(n)) %>%
  ungroup() %>%
  group_by(sim) %>%
  mutate(share_n = n / sum(n) * 100) %>%
  ungroup() %>%
  filter(risk_cat == "high")
strMinorVsHigh <- paste0("Total risk attendees: ", 
                         round_k(mean(transRisk_MinorVsHigh$n), 0),
                         " \u00B1 ",
                         round_k(sd(transRisk_MinorVsHigh$n), 0),
                         " (",
                         round_k(mean(transRisk_MinorVsHigh$share_n), 1),
                         "% \u00B1 ",
                         round_k(sd(transRisk_MinorVsHigh$share_n), 1),
                         "%)")
transRisk_high <- transRisk_qq %>%
  dplyr::filter(risk_cat %in% group_labs) 
transRisk_qq_pl <- transRisk_high %>%
  mutate(risk_cat = factor(risk_cat, group_labs)) %>%
  ggplot(aes(x = risk_cat, y = n, fill = risk_cat)) +
  stat_boxplot(geom ='errorbar', width = .2) +
  geom_boxplot(width = .2, outlier.shape = NA) +
  annotate("text", x = .5, y = 18.5, label = strMinorVsHigh, size = 8 / cm(1), hjust = 0, vjust = 0) +
  scale_y_continuous(sec.axis = sec_axis(~ . / nrow(transRisk_indv), labels = scales::percent, name = "Proportion of attendees"),
                     expand = c(0,0), limits = c(0,20)) +
  scale_fill_manual(values = wes_palette("Darjeeling2")) +
  labs(x = "Risk of infection", y = "Number of attendees") +
  theme_bw2() +
  theme(legend.position = "none")
save_plot(transRisk_qq_pl, pdf_file = "../results/modeling/high-risk-of-infection.pdf", w = aw, h = ah)
```

@@

```{r}
# average quanta concentration
quantaDF_av <- sim_results %>%
  mutate(daytime = ifelse(hhmm <= "12:00", "Morning", "Afternoon"),
         daytime = factor(daytime, levels = c("Morning", "Afternoon"))) %>%
  group_by(daytime, id, location) %>%
  summarize(N = mean(N)) %>%
  ungroup()

a_ac_grid = -9
quantaDF_av_wr <- quantaDF_av %>%
  group_by(daytime) %>%
  head(nrow(waiting_room_df)) %>%
  mutate(id = as.character(id)) %>%
  ungroup() %>%
  left_join(waiting_room_df, by = c("id")) %>%
  rename(x = long, y = lat) %>%
  rotate_xy(a_ac_grid)
quantaDF_av_pa <- quantaDF_av %>%
  group_by(daytime) %>%
  tail(nrow(passage_df)) %>%
  mutate(id = as.character(1:n())) %>%
  ungroup() %>%
  left_join(passage_df, by = c("id")) %>%
  rename(x = long, y = lat) %>%
  rotate_xy(a_ac_grid)
quantaDF_av_tb <- quantaDF_av %>%
  filter(location == "tb room") %>%
  group_by(daytime) %>%
  mutate(id = as.character(1:n())) %>%
  ungroup() %>%
  left_join(tb_room_df, by = c("id")) %>%
  rename(x = long, y = lat) %>%
  rotate_xy(a_ac_grid)

qc_pl <- ggplot(mapping = aes(x = x, y = y, group = group, fill = N)) +
  geom_polygon(data = quantaDF_av_wr) +
  geom_polygon(data = quantaDF_av_pa) +
  geom_polygon(data = quantaDF_av_tb) +
  coord_fixed() +
  #scale_fill_stepsn(colours = RColorBrewer::brewer.pal(n = 9, name = "YlOrRd")[c(1,3,5,7,9)], breaks = seq(1,6,1)*1e-6, limits = c(0,100), na.value = NA) +
  facet_wrap(~daytime, ncol = 1)
qc_pl
qc_pl <- spatial_ggpl(qc_pl)

qc_pl
save_plot(qc_pl, pdf_file = "../results/modeling/quanta-concentration.pdf", w = aw, h = 2*ah)
```

>>>>

```{r}
selected_dates <- list.files("../simulations/Masi/")
selected_dates <- as.Date(selected_dates[!grepl("old", selected_dates)])
```

```{r}
# overview
files_by_date <- data.frame(
  directory = list.files("../data-clean/Masi/combined-data", full.names = T)
) %>%
  mutate(date = basename(directory),
         files_in_dir = map(directory, list.files),
         Clinical = map_lgl(files_in_dir, function(x) any(grepl("clinical", x))),
         CO2 = map_lgl(files_in_dir, function(x) any(grepl("environmental", x))),
         Tracking = map_lgl(files_in_dir, function(x) any(grepl("tracking", x))))

files_by_date %>%
  dplyr::select(date, Clinical, CO2, Tracking) %>%
  reshape2::melt("date") %>%
  ggplot(aes(x = variable, y = date, fill = value)) +
  geom_tile() +
  labs(x = "Dataset", fill = "Available") +
  scale_fill_manual(values = wes_palette("Chevalier1")[c(2,1)]) +
  theme_classic() +
  theme(axis.title.y = element_blank())
ggsave(filename = "../insights/data-check-dataset-availability.pdf", width = 16 / cm(1), height = 21 / cm(1))
```

@@

# share of TB patients
share_tb <- clinical_dta  %>%
  group_by(date, patient_id) %>%
  summarize(tb = any(tb_suspect == "yes")) %>%
  ungroup() %>%
  group_by(date) %>%
  summarize(n = n(),
            n_tb = sum(tb)) %>%
  arrange(date) %>%
  mutate(prop_tb = n_tb / n * 100,
         date = format(date, format = "%b %d"),
         date = factor(date, levels = unique(date))) %>%
  ungroup() 
share_tb_pl <- share_tb %>%
  ggplot(aes(x = date, y = n_tb)) +
  geom_bar(stat = "identity", fill = "grey", color = "black", width = .5) +
  annotate("text", x = "Nov 12", y = mean(share_tb$n_tb), label = paste0("Mean = ",round(mean(share_tb$n_tb), 1)), color = "darkred", size = 8 / cm(1), vjust = -1) +
  geom_hline(aes(yintercept = mean(share_tb$n_tb)), color = "darkred") +
  scale_y_continuous(expand = expansion(mult = c(0,0.05))) +
  scale_x_discrete(breaks = format(selected_dates, format = "%b %d")[c(1, 4, 8, 12)]) +
  labs(y = "Number of masked TB patients") +
  theme_classic() +
  theme(axis.title.x = element_blank(),
        plot.margin = margin(5.5, 5.5, 5.5, 5.5),
        text = element_text(size = text_descr))
share_tb_pl
ggsave(plot = share_tb_pl, filename = "../doc/IWHOD/presentation/figures/share-tb-patients.png", w = width_descr, h = height_descr)
```

@@

```{r}
co2_pl <- readRDS("../data-clean/Masi/environmental-data/co2-temp-humid.rds") %>%
  filter(location %in% c("waiting room", "tb room"),
         date %in% selected_dates) %>%
  mutate(location = factor(ifelse(location == "tb room", "TB room", "Waiting room"), levels = c("Waiting room", "TB room")),
         time = as.POSIXct(time, format = "%H:%M", tz = "CET")) %>%
  ggplot(aes(x = time, y = co2, color = location, fill = location)) +
  stat_lineribbon(alpha = .25, size = .75) +
  scale_x_datetime(expand = c(0,0), date_breaks = "2 hours", date_labels = "%H:%M") +
  scale_y_continuous(expand = c(0,0), breaks = scales::breaks_width(width = 100)) +
  scale_fill_manual(values = wes_palette("Moonrise2")) +
  scale_color_manual(values = wes_palette("Moonrise2")) +
  labs(y = expression("CO"[2]*" (ppm)"), fill = "Quantile", color = "Quantile") +
  theme_classic() +
  theme(legend.position = c(.65,.95), legend.direction = "horizontal", legend.key.width = unit(0.3, "cm"), legend.key.height = unit(0.2, "cm"),
        plot.margin = margin(5.5, 5.5, 5.5, 5.5), axis.title.x = element_blank(), legend.title = element_blank(),
        text = element_text(size = text_descr)) 
co2_pl
ggsave(plot = co2_pl, filename = "../doc/IWHOD/presentation/figures/co2-levels.png", width = width_descr, height = height_descr)
```

@@

# test
# waiting_room_df$value <- rnorm(nrow(waiting_room_df))
# passage_df$value <- rnorm(nrow(passage_df))
# tb_room_df$value <- rnorm(nrow(tb_room_df))
# 
# ggplot(mapping = aes(x = long, y = lat, group = group, fill = value)) +
#   geom_polygon(data = waiting_room_df) +
#   geom_polygon(data = passage_df) +
#   geom_polygon(data = tb_room_df) +
#   ggpubr::background_image(clinic_img) +
#   annotate("text", x = -13200, y = -5300, label = "Entrance", size = 8 / cm(1), fontface = 2, hjust=0,vjust=0) +
#   annotate("text", x = -13400, y = -2300, label = "Waiting room", size = 8 / cm(1), fontface = 2, hjust=0,vjust=0) +
#   annotate("text", x = -5000, y = -4100, label = "Registration", size = 8 / cm(1), fontface = 2, angle = 90, hjust=0,vjust=0) +
#   annotate("text", x = 2600, y = -2700, label = "TB room", size = 8 / cm(1), fontface = 2) +
#   scale_y_continuous(expand = expansion(add=c(2500, 4000))) +
#   scale_x_continuous(expand = expansion(add=c(400, 500))) +
#   labs(fill = "Density") +
#   theme(axis.text = element_blank(), axis.title = element_blank(), axis.ticks = element_blank(),
#         legend.position = c(0.825,0.075), legend.direction = "horizontal", legend.title = element_blank(), #legend.title = element_text(vjust = .75),
#         panel.background = element_rect(fill = RColorBrewer::brewer.pal(n = 3, name = "YlOrRd")[1]), panel.grid.major = element_blank(),
#         panel.grid.minor = element_blank())
```

@@

```{r}
no_people <- do.call(rbind, lapply(selected_dates, function(x) readRDS(paste0("../data-clean/Masi/combined-data/", x, "/tracking-linked-clinical-data.rds")))) %>%
  mutate(date = as.Date(format(time, format = "%Y-%m-%d")),
         time_min = as.POSIXct(format(time, format = "%H:%M"), format = "%H:%M"))

@@

# Spatial
no_people_spatial_pl <- no_people %>%
  ggplot(aes(x = x, y = y)) +
  geom_bin2d(binwidth = 100) +
  scale_fill_stepsn(colours = RColorBrewer::brewer.pal(n = 9, name = "YlOrRd"), trans = "log", breaks = c(1, 10, 100, 1000, 10000), labels = function(x) signif(x / nrow(no_people_time) * 60 * 24, 1)) +
    ggpubr::background_image(clinic_img) +
    annotate("text", x = -13200, y = -5800, label = "Entrance", size = text_descr / cm(1), hjust=0,vjust=0) +
    annotate("text", x = -14000, y = -2600, label = "Waiting room", size = text_descr / cm(1), hjust=0,vjust=0) +
    annotate("text", x = -5800, y = -4500, label = "Registration", size = text_descr / cm(1), angle = 90, hjust=0,vjust=0) +
    annotate("text", x = 3000, y = -2700, label = "TB room", size = text_descr / cm(1)) +
    scale_y_continuous(expand = expansion(mult=c(0.05, 0.215))) +
    scale_x_continuous(expand = expansion(mult=c(0.03, 0))) +
    labs(fill = "Density (#tracks/day)") +
    theme(axis.text = element_blank(), axis.title = element_blank(), axis.ticks = element_blank(), legend.key.width = unit(0.3, "cm"), legend.key.height = unit(0.3, "cm"),
          legend.position = c(0.825,0.075), legend.direction = "horizontal",legend.title = element_text(vjust = .75),
          panel.background = element_rect(fill = RColorBrewer::brewer.pal(n = 9, name = "YlOrRd")[1]), panel.grid.major = element_blank(),
          panel.grid.minor = element_blank()) +
  guides(fill = guide_legend(title.position = "top", label.position = "bottom"))
no_people_spatial_pl
ggsave(plot=no_people_spatial_pl, filename = "../doc/IWHOD/presentation/figures/no-people-spatial.png", width = width_descr, height = height_descr)
```

@@

```{r}
relQC_pl <- expand.grid(distance = seq(0, 10, .1), 
                           mu = rMuIc(n_samples)) %>%
  mutate(relQC = dIc(distance, mu) * 100) %>%
  ggplot(aes(x = distance, y = relQC)) +
  stat_lineribbon(alpha = .5, size = .5) +
  scale_x_continuous(expand = c(0,0), limits = c(0, 10), breaks = seq(0, 10, 2)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,100)) +
  scale_fill_brewer(palette = "OrRd") +
  labs(x = "Distance (m)", y = "Rel. prob. (%)", fill = "Quantile") +
  theme_classic() +
  theme(legend.position = c(.9,.85), legend.direction = "vertical", legend.key.width = unit(0.3, "cm"), legend.key.height = unit(0.2, "cm"),
        legend.spacing.y = unit(.1, "cm"),
        plot.margin = margin(5.5, 10, 5.5, 5.5),
        text = element_text(size = text_descr),
        legend.title = element_blank()) +
  guides(fill = guide_legend(title.position = "top", byrow = T))
ggsave(plot = relQC_pl, filename = "../doc/IWHOD/presentation/figures/spatial-relative-quanta-concentration.png", width = width_descr * 0.66, height = height_descr * 0.66)
```

@@

@@

```{r}
# transmission risk 
sim_files <- sapply("../simulations/Masi", list.files, full.names = T) 
sim_files <- unlist(sapply(sim_files, list.files, full.names = T))
tr_files <- sim_files[grepl("TR", sim_files)]

average_transRisk <- function(file) {
  # quanta concentration and transmission risk
  qctr <- readRDS(file)

  # individual patient transmission risk by simulation
  tr <- qctr %>%
    group_by(patient_id, date, sim) %>%
    slice(1) %>%
    ungroup()

  return(tr)
}

transRisk <- parallel::mclapply(tr_files, average_transRisk, mc.cores = 6)
transRisk <- do.call(rbind, transRisk)

transRisk_av <- transRisk %>%
    group_by(date, sim) %>%
    summarize(across(c(P_N, P_N_ns), mean)) %>%
    ungroup()

transRisk_av_daily <- transRisk_av %>%
  group_by(date) %>%
  summarize(across(c(P_N, P_N_ns), list(m = mean, s = sd))) %>%
  ungroup()

mean_risk_daily <- round(mean(transRisk_av_daily$P_N_m * 100), 2)
range_daily <- round(range(transRisk_av_daily$P_N_s * 100), 2)
message(sprintf("Spatiotemporal transmission risk across clinical attendee: %s (range: %s percent to %s percent)", mean_risk_daily, range_daily[1], range_daily[2]))

# high risk patients
transRisk_high <- transRisk %>%
  mutate(high_risk = ifelse(P_N > 0.01, 1, 0),
         date = as.Date(date)) %>%
  group_by(date, sim) %>%
  summarize(n_risk = sum(high_risk)) %>%
  ungroup() %>%
  group_by(sim) %>%
  arrange(desc(date)) %>%
  mutate(date_letter = factor(LETTERS[2:(n()+1)], levels = LETTERS[1:(length(selected_dates)+1)])) %>%
  ungroup()

transRisk_high_daily <- transRisk_high %>%
  group_by(date_letter) %>%
  summarize(n_risk_m = mean(n_risk),
            n_risk_s = sd(n_risk),
            n_risk_l = quantile(n_risk, 0.025),
            n_risk_u = quantile(n_risk, 0.975)) %>%
  ungroup()

transRisk_high_daily_av <- data.frame(
  n_risk_m = mean(transRisk_high_daily$n_risk_m),
  n_risk_s = sd(transRisk_high_daily$n_risk_m)) %>%
  mutate(n_risk_u = n_risk_m + qnorm(.975) * n_risk_s,
         n_risk_l = n_risk_m + qnorm(.025) * n_risk_s,
         date_letter = factor(LETTERS[1], levels = LETTERS[1:(length(selected_dates)+1)]),
         n_risk_l = ifelse(n_risk_l < 0, 0, n_risk_l))

ylabs <- c("Average", rev(format(as.Date(selected_dates), format = "%b %d")))

highRiskPat_pl <- ggplot() +
  geom_vline(aes(xintercept = mean(transRisk_high_daily$n_risk_m)), linetype = "dotted", color = "darkred") +
  stat_pointinterval(data = transRisk_high, mapping = aes(x = n_risk, y = date_letter, slab_color = after_stat(level)), 
                    point_interval = "mean_qi", .width = c(.5, .9), point_size = 2, fill = "white", shape = 21, point_color = "darkred") +
  geom_errorbar(data = transRisk_high_daily_av, mapping = aes(xmin = n_risk_l, xmax = n_risk_u, y = date_letter),
                width = .2, color = "darkred") +
  geom_point(data = transRisk_high_daily_av, mapping = aes(x = n_risk_m, y = date_letter),
             shape = 23, color = "darkred", fill = "white", size = 4) +
  scale_color_manual(values = scales::brewer_pal()(3)[-1], aesthetics = "slab_color") +
  scale_x_continuous(expand = c(0.01,0)) +
  scale_y_discrete(breaks = LETTERS[1:(nrow(transRisk_high_daily)+1)], labels = ylabs) +
  labs(x = "Number of attendees") +
  theme_classic() +
  theme(text = element_text(size = text_descr),
        axis.title.y = element_blank(), 
        legend.position = "none")

tab_data <- rbind(transRisk_high_daily, transRisk_high_daily_av) %>%
  mutate(meanCI = paste0(add_ws(round(n_risk_m, 0)), " [", add_ws(round(n_risk_l, 0), n = 1), ", ", add_ws(round(n_risk_u, 0)), "]"))
tab_base <- ggplot(data = tab_data, aes(y = date_letter)) +
    ylab(NULL) + xlab("  ") + 
    theme(plot.title = element_text(hjust = 0, face = 2), ## centering title on text
        axis.text.x=element_text(color="white"), ## need text to be printed so it stays aligned with figure but white so it's invisible
        axis.line=element_blank(),
        axis.text.y=element_blank(),axis.ticks=element_blank(),
        axis.title.y=element_blank(),legend.position="none",
        panel.background=element_blank(),panel.border=element_blank(),panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),plot.background=element_blank())
summary_tab <- tab_base +
  geom_text(aes(x = 0, label = meanCI), size = text_descr / cm(1)) +
  ggtitle("Mean (95%-UI)")

highRiskPat_pl_wTable <- grid.arrange(highRiskPat_pl, summary_tab, ncol = 2, heights = height_descr, widths = width_descr * c(0.7,.3))
ggsave(plot = highRiskPat_pl_wTable, filename = "../doc/IWHOD/presentation/figures/high-risk-patients.png", width = width_descr * 1.5, height = height_descr * 1.5)
```

@@

```{r}
# files
qc_files <- sim_files[grepl("QC", sim_files)]

average_quantaConc <- function(file) {
  # quanta concentration and transmission risk
  qctr <- readRDS(file)

  # average quanta concentration
  quantaDF_av <- qctr %>%
    mutate(daytime = ifelse(format(time, "%H:%M") <= "12:00", "Morning", "Afternoon"),
           daytime = factor(daytime, levels = c("Morning", "Afternoon"))) %>%
    group_by(date, daytime, id, location) %>%
    summarize(N = mean(N, na.rm = T)) %>%
    ungroup()

  return(quantaDF_av)
}

quantaConc <- parallel::mclapply(qc_files, average_quantaConc, mc.cores = 6)
quantaConc <- do.call(rbind, quantaConc)

quantaConc_av <- quantaConc %>%
  group_by(date, daytime, location, id) %>%
  summarize(N = mean(N, na.rm = T)) %>%
  ungroup() %>%
  group_by(daytime, location, id) %>%
  summarize(N = mean(N, na.rm = T)) %>%
  ungroup()

quantaConc_av_wr <- quantaConc_av %>%
  mutate(id = as.character(id)) %>%
  dplyr::filter(location == "waiting room",
                id %in% unique(waiting_room_df$id)) 
quantaConc_av_wr <- left_join(waiting_room_df, quantaConc_av_wr, by = c("id"))
n_pa_ids <- max(as.numeric(passage_df$id))
quantaConc_av_pa <- quantaConc_av %>%
  group_by(daytime) %>%
  arrange(id) %>%
  slice((n()-n_pa_ids+1):n()) %>%
  mutate(id = as.character(1:n())) %>%
  ungroup() 
quantaConc_av_pa <- left_join(passage_df, quantaConc_av_pa, by = c("id"))
quantaConc_av_tb <- quantaConc_av %>%
  filter(location == "tb room") %>%
  group_by(daytime) %>%
  mutate(id = as.character(1:n())) %>%
  ungroup() 
quantaConc_av_tb <- left_join(tb_room_df, quantaConc_av_tb, by = c("id"))

entrance_lab <- textGrob(label = "Entrance", x = 0.1, y = 0.165, gp = gpar(size = text_descr / cm(1)), just = c("left"))
wr_lab <- textGrob(label = "Waiting room", x = 0.05, y = 0.45, gp = gpar(size = text_descr / cm(1)), just = c("left"))
tb_lab <- textGrob(label = "TB room", x = 0.75, y = 0.4, gp = gpar(size = text_descr / cm(1)), just = c("left"))
re_lab <- textGrob(label = "Registration", x = 0.44, y = 0.25, gp = gpar(size = text_descr / cm(1)), just = c("left"), rot = 90)

qc_pl <- ggplot(mapping = aes(x = long, y = lat, group = group, fill = N)) +
  geom_polygon(data = quantaConc_av_wr) +
  geom_polygon(data = quantaConc_av_pa) +
  geom_polygon(data = quantaConc_av_tb) +
  ggpubr::background_image(clinic_img) +
  scale_fill_stepsn(colours = RColorBrewer::brewer.pal(n = 9, name = "YlOrRd"), trans = "log1p", labels = function(x) x * 1000, breaks = c(.1, .5, 1, .15, 2)/1000) +
  scale_y_continuous(expand = expansion(add=c(2500, 3250))) +
  scale_x_continuous(expand = expansion(add=c(400, 500))) +
  facet_wrap(~daytime, ncol = 1) +
  annotation_custom(entrance_lab, xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf) +
  annotation_custom(wr_lab, xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf) +
  annotation_custom(tb_lab, xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf) +
  annotation_custom(re_lab, xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf) +
  labs(fill = expression("Density (10"^-3*"quanta/m"^3*")")) +
  theme_classic() +
  theme(text = element_text(size = text_descr),
        axis.text = element_blank(), axis.title = element_blank(), axis.ticks = element_blank(),
        legend.position = c(0.825,0.05), legend.direction = "horizontal", legend.key.width = unit(0.3, "cm"), legend.key.height = unit(0.2, "cm"),
        panel.background = element_rect(fill = RColorBrewer::brewer.pal(n = 9, name = "YlOrRd")[1]), panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  guides(fill = guide_legend(title.position = "top"))
qc_pl
ggsave(plot = qc_pl, filename = "../doc/IWHOD/presentation/figures/quanta-concentration.png", width = width_descr * 1.5, height = height_descr * 2)
```
